%----------------------------------------------------------
%	Packages and document configurations
%----------------------------------------------------------


\documentclass[fontsize=10pt]{scrartcl}


\usepackage[hmargin=1.25cm,vmargin=1.25cm,twocolumn,columnsep=1.25cm]{geometry}
\usepackage{
	bookman,
	fontawesome,
	needspace,
	hyperref,
	pifont,
	tabularx,
	xcolor
}

\pagestyle{empty}
\setcounter{secnumdepth}{-1}
\setlength\parindent{0pt}
\setkomafont{section}{\scshape\Large\mdseries}
\setkomafont{disposition}{\color[HTML]{801010}}
\definecolor{link}{HTML}{506060} % Hyperlinks
\hypersetup{colorlinks,breaklinks,urlcolor=link,linkcolor=link}


%----------------------------------------------------------
%	Macros
%----------------------------------------------------------


% Overriding section command
\let\oldsection\section
\renewcommand\section[2][]{%
	\vspace{-5px}
    \oldsection[#1]{#2}%
    \newdimen\raising%
    \raising=\dimexpr-0.7\baselineskip\relax%
    \vskip\raising\hrule height 0.5pt\vskip-\raising
}

% Date, position name, company name
\newcommand\position[3]{
	\vspace{5px}
	{\raggedleft\textsc{#1}\\[2.5pt]}%
	{\raggedright{\large \textbf{#2}}\\[2.5pt]%
	\normalsize{\textit{#3}}\\[5pt]}%
}
    
    
%----------------------------------------------------------
%	Document
%----------------------------------------------------------


\begin{document}

\twocolumn[
	\begin{center}
		\vskip-\lastskip
		{\usekomafont{part} Martynas Subonis}\\
		{\selectfont\large \textit{
			I enjoy creating impactful software. Interested in software engineering/data science opportunities in Z{\"u}rich.
		}}
	\end{center}]



\needspace{0.5\textheight}
\newdimen\boxwidth
\boxwidth=\dimexpr\linewidth-2\fboxsep\relax
\colorbox[HTML]{F5DD9D}{
	\begin{tabularx}{\boxwidth}{c|X}
		\raisebox{-2pt}{\Large\ding{41}} & \href{mailto:martynas.subonis@gmail.com}{martynas.subonis@gmail.com}\smallskip\\
		\faLinkedin                      & \href{https://www.linkedin.com/in/martynassubonis}{linkedin.com/in/martynassubonis}\smallskip \\
		\raisebox{-1pt}{\Large\ding{37}} & {+41792802648}\smallskip\\
	\end{tabularx}
}


\section{Work Experience}
\position{2019 November -- 2022 September}{Full Stack Software Engineer}{True Wealth AG, Z{\"u}rich}
\normalsize{
	Software engineer at a leading wealth management company in Switzerland. While working at True Wealth, I had responsibilities of:
	\begin{itemize}
		\item{Leading the implementation of a trade-volume optimization pipeline for a new product stream. The optimization algorithm consisted of transforming
		            product regulations into mathematical constraints and expressing the business problem as a convex optimization problem. The overall pipeline 
		            additionally included relational data modeling, data processing, and exposing new functionality via RESTful APIs.}
		\item{Co-leading new portfolio risk model. Solely responsible for mathematical models, \\contributed to new RESTful APIs,
		            risk database model, customer risk data migration, and frontend integration/redesign. Estimated impact -- improved portfolio 
		            risk estimation and granularization for 10000+ customers.}
		\item{Implementing client-data anonymization process. The pipeline would anonymize $\approx$400 GB of sensitive client data daily,
		            providing risk-free production-like data for development/\\testing.}
		\item{Co-leading website redesign. The redesign focused on performance, accessibility, and SEO. As a result, each page had
		            100\% SEO and $\geq$ 93\% performance/accessibility scores on Lighthouse reports.}
		\item{Integration of E2E tests into the CI pipeline and build-system optimizations.}
	\end{itemize}
}

\textbf{Tech-stack} included: \textsc{Java}, \textsc{TypeScript}, \textsc{Python}, \textsc{React.js}, \textsc{Next.js}, \textsc{Docker}, 
\textsc{PostgreSQL}, \textsc{GCP}, \textsc{git}, \textsc{Gradle},  \textsc{Cypress}, \textsc{Webpack}.

\position{2018 July -- 2019 October}{Full Stack Software Engineer}{atfinity GmbH, Z{\"u}rich}
\normalsize{
	Software developer at a digital finance solutions company. Contributor to the main product - \textit{regfinity} compliance platform. Main responsibilities included:
	\begin{itemize}
		\setlength\itemsep{0pt}
		\item{Supporting the creation of software specifications and architectures.}
		\item{Developing RESTful backend APIs of the platform.}
		\item{Contributing to the development of a rule evaluation system.}
		\item{Creating interactive user interfaces.}
		\item{Defining quality assurance processes and conducting technical interviews.}
	\end{itemize}
}

\textbf{Tech-stack} included: \textsc{Python}, \textsc{JavaScript}, \textsc{React.js}, \textsc{Django}, \textsc{MySQL}, 
\textsc{Docker}, \textsc{git}, \textsc{Gradle}, \textsc{Webpack}, \textsc{Redux}.

\position{2015 July -- 2015 August}{Research Assistant}{Institute of Theoretical Physics and Astronomy -- Department of Nuclei Theory, Vilnius University, Vilnius}
\normalsize{
	Part of the project ``Subatomic particle physics at CERN CMS experiment''. Under the two-Higgs-doublet model (2HDM), created tools 
	for data analysis and visualization with a \textsc{C++} modular scientific software framework \textsc{ROOT}.
}


\section{Research Experience}
\position{2016 -- 2017}{Bayesian Optimization For Likelihood-Free Inference}{School of Informatics, The University of Edinburgh, Edinburgh}
\normalsize{
	Analyzed high-dimensional Bayesian optimization (BO) with \\ Bayesian neural networks for likelihood-free inference (LFI). 
	Utilizing \textsc{Python}, created BO algorithm based on Bayesian neural networks for LFI, which outperformed standard Gaussian 
	processes in both accuracy and computational cost aspects.
}


\position{2015 -- 2016}{Representation of Molecular Charge Density}{Theoretical Physics Department, Faculty of Physics, Vilnius University, Vilnius}
\normalsize{
	Investigated the representation of molecular charge density by point charges using numerical optimization algorithms. Created 
	a continuous space optimization algorithm based on simulated annealing, for derivative-free optimization. Mainly \textsc{MATLAB} was 
	used. Analyzed the molecular distance at which the point charge approximation becomes invalid.
}

\newpage
\section{Education}


\begin{tabular}{rl}
	2016 -- 2017 & {\large\textsc{Master of Science}}\\
	             & {\large\textbf{Data Science}}\\
	             & Distinction\\
	             & \textit{The University of Edinburgh, UK}\\
	             & \small Focus on machine learning, data analysis\\
	             & \small and Bayesian optimization.\\[5pt]
	2012 -- 2016 & {\large\textsc{Bachelor of Science}}\\
	             & {\large\textbf{Physics}}\\
	             & Overall mark -- 89\%\\
	             & \textit{Vilnius University, Lithuania}\\
	             & \small Focus on math and theoretical physics.\\[5pt]
	2015 -- 2016 & {\large\textsc{Exchange Studies}}\\
	             & {\large\textbf{Physics}}\\
	             & \textit{Lund University, Sweden}\\
	             & \small Focus on math, computational physics\\
	             & \small and machine learning.                        
\end{tabular}


\section{Academic Awards}
\begin{tabular}{rl}
	2017 & \textbf{MSc Class Award: Distinction}\\
	     & \textit{Awarded for excellent academic}\\
	     & \textit{performance during Master of Science}\\
	     & \textit{studies}.\\[5pt]
	2016 & \textbf{The University of Edinburgh UK/EU}\\ 
	     & \textbf{Master's Scholarship}\\
	     & \textit{Awarded on the basis of academic merit.}
\end{tabular}


\section{Technical Skills}
{\raggedright{\textbf{Programming Languages}}\\
Python, TypeScript, Java, SQL, MATLAB
\vspace{5px}

{\raggedright{\textbf{Web}}\\
React.js, Next.js, HTML, CSS, Django, Flask, Express.js, Webpack, Tailwind
\vspace{5px}

{\raggedright{\textbf{DevOps}}\\
git, Docker, K8s, CI/CD, GitHub Actions, gradle, bash
\vspace{5px}

{\raggedright{\textbf{Machine Learning}}\\
Scikit-learn, SciPy, Keras, TensorFlow, PyTorch


\section{Online Education}
 
 
 {\raggedright{\large \textbf{TensorFlow in Practice}}\\
  \normalsize{\textit{TensorFlow Specialization by \href{https://www.deeplearning.ai/tensorflow-in-practice/}{Andrew Ng}
		  (\href{https://www.deeplearning.ai/tensorflow-in-practice/}{deeplearning.ai})}}}\\[5pt]
\normalsize{Best practices of using TensorFlow for computer vision, natural language processing,  sequence/time series problems.}

{\raggedright{\large \textbf{Deep Learning}}\\
	\normalsize{\textit{Deep Learning Specialization by \href{https://www.deeplearning.ai/deep-learning-specialization/}{Andrew Ng}\\
			(\href{https://www.deeplearning.ai/deep-learning-specialization/}{deeplearning.ai})}}}\\[5pt]
\normalsize{Foundations of Deep Learning. Convolutional networks, RNNs, LSTM, Adam, Dropout, BatchNorm, Xavier/He initialization etc.}

\vspace{40px}
\section{Communication skills}

\begin{itemize}
	\item Lithuanian - Native
	\item English - C2
	\item German - A1
	\item Russian - A2
\end{itemize}


\end{document}